Identifying and correcting for misspecifications\\in GWAS summary statistics and polygenic scores

### 2022-08-05 paper/paper-misspec.tex
typo
add title to fig

\begin{figure}[!h]
	\centerline{\includegraphics[width=0.95\textwidth]{brca_onco_qc}}
	\caption{Standard deviations inferred from the OncoArray breast cancer GWAS summary statistics using equation \eqref{eq:approx-sd-log} (\textbf{A:} Raw or \textbf{B:} dividing them by $\sqrt{\text{INFO}}$) versus the ones inferred from the reported GWAS allele frequencies $f_j$ (using $\sqrt{2 f_j (1 - f_j)}$). Only 100,000 HapMap3 variants are represented, at random.}
	\label{fig:brca_onco_qc}
\end{figure}

@@

\clearpage
%\vspace*{3em}

@@

%\clearpage
\vspace*{3em}

>>>>

\begin{figure}[!h]
	\centerline{\includegraphics[width=0.95\textwidth]{brca_onco_qc}}
	\caption{Comparison of standard deviations for quality control of GWAS summary statistics. Standard deviations inferred from the OncoArray breast cancer GWAS summary statistics using equation \eqref{eq:approx-sd-log} (\textbf{A:} Raw or \textbf{B:} dividing them by $\sqrt{\text{INFO}}$) versus the ones inferred from the reported GWAS allele frequencies $f_j$ (using $\sqrt{2 f_j (1 - f_j)}$). Only 100,000 HapMap3 variants are represented, at random.}
	\label{fig:brca_onco_qc}
\end{figure}

@@

%\clearpage
%\vspace*{3em}

@@

%\clearpage
%\vspace*{3em}
